\documentclass[10pt,a4paper]{article}
\usepackage[utf8]{inputenc}\usepackage[T1]{fontenc}\usepackage{mathptmx}
\usepackage[margin=0.8cm]{geometry}\usepackage{enumitem}\usepackage{tabularx}
\usepackage{array}\usepackage{booktabs}\usepackage{fancyhdr}\usepackage{setspace}
\usepackage{tikz}\usepackage{amssymb}
\pagestyle{fancy}\fancyhf{}
\fancyhead[L]{\small\textbf{AIGGPA Research Schedule}}\fancyhead[R]{\small Respondent ID: \_\_\_\_\_\_\_\_}
\fancyfoot[C]{\small Page \thepage}\renewcommand{\headrulewidth}{0.5pt}
\setlength{\headheight}{14pt}\setstretch{1.1}
\newcolumntype{L}[1]{>{\raggedright\arraybackslash}p{#1}}
\newcommand{\qbox}[1]{\noindent\textbf{#1}\par\vspace{2pt}\noindent\hrulefill\par\vspace{3pt}}
\newcommand{\likert}{{\Large$\square$}\,1\quad{\Large$\square$}\,2\quad{\Large$\square$}\,3\quad{\Large$\square$}\,4\quad{\Large$\square$}\,5}
\newcommand{\yesno}{{\Large$\square$}\,Yes\quad{\Large$\square$}\,No}
\newcommand{\blank}{\rule{8cm}{0.4pt}}
\begin{document}

% ── COVER / HEADER PAGE ──
\begin{center}
{\Large\bfseries AIGGPA FIELD RESEARCH SCHEDULE}\\[2pt]
{\small Assessment of Digital Tool Usage Among Government Employees}\\[2pt]
{\small Atal Bihari Vajpayee Institute of Good Governance \& Policy Analysis, Bhopal}
\end{center}
\vspace{4pt}
\noindent\rule{\textwidth}{1pt}
\vspace{4pt}

\noindent\begin{tabularx}{\textwidth}{@{}L{7cm} L{7cm}@{}}
\textbf{Respondent ID:} \blank & \textbf{Date:} \_\_\_/\_\_\_/2026 \\[8pt]
\textbf{Department:} {\Large$\square$} Revenue\quad{\Large$\square$} Rural Dev\quad{\Large$\square$} Forest\quad{\Large$\square$} Health & \textbf{Office:} {\Large$\square$} Head Office\quad{\Large$\square$} District Office \\[8pt]
\textbf{Interviewer:} \blank & \textbf{Start Time:} \_\_:\_\_\quad\textbf{End Time:} \_\_:\_\_ \\
\end{tabularx}

\vspace{4pt}\noindent\rule{\textwidth}{0.5pt}\vspace{4pt}

% ═══════════════════════════════════
% SECTION A: DEMOGRAPHICS
% ═══════════════════════════════════
\noindent{\large\bfseries Section A: Respondent Profile}\vspace{3pt}

\noindent\begin{tabularx}{\textwidth}{@{}L{0.5cm} L{8cm} X@{}}
Q1 & Designation / Post: & \blank \\[3pt]
Q2 & Job Role / Level: & \blank \\[3pt]
Q3 & Age group: & {\Large$\square$} Below 30\quad{\Large$\square$} 30--45\quad{\Large$\square$} 46--60 \\[3pt]
Q4 & Gender: & {\Large$\square$} Male\quad{\Large$\square$} Female\quad{\Large$\square$} Other \\[3pt]
Q5 & Years of service: & {\Large$\square$} 0--5\quad{\Large$\square$} 6--10\quad{\Large$\square$} 11--20\quad{\Large$\square$} 21+ \\[3pt]
Q6 & Highest education: & {\Large$\square$} Up to 12th\quad{\Large$\square$} Graduate\quad{\Large$\square$} Post-Graduate\quad{\Large$\square$} Professional \\
\end{tabularx}

\vspace{4pt}
% ═══════════════════════════════════
% SECTION B: FACILITATING CONDITIONS
% ═══════════════════════════════════
\noindent{\large\bfseries Section B: Infrastructure \& Facilitating Conditions}\vspace{4pt}

\small\textit{Likert Scale: 1=Strongly Disagree / Very Poor \quad 2=Disagree / Poor \quad 3=Neutral \quad 4=Agree / Good \quad 5=Strongly Agree / Excellent}\vspace{3pt}

\noindent\begin{tabularx}{\textwidth}{@{}L{0.5cm} X L{5.5cm}@{}}
Q7 & What digital devices are available at your workstation? & {\Large$\square$} Desktop {\Large$\square$} Laptop {\Large$\square$} Tablet {\Large$\square$} Phone {\Large$\square$} None \\[3pt]
Q8 & Do you share your device with other employees? & {\Large$\square$} Yes, always {\Large$\square$} Sometimes {\Large$\square$} No, dedicated \\[3pt]
Q9 & Rate internet connectivity at your office: & \likert \\[3pt]
Q10 & How often do you experience internet outages per week? & {\Large$\square$} Never {\Large$\square$} 1--2 {\Large$\square$} 3--5 {\Large$\square$} Daily \\[3pt]
Q11 & Is IT helpdesk / technical support available? & \yesno \\[3pt]
Q12 & If yes, how quickly are issues resolved? & {\Large$\square$} Same day {\Large$\square$} 2--3 days {\Large$\square$} 1 week+ {\Large$\square$} Never resolved \\
\end{tabularx}

\vspace{4pt}
% ═══════════════════════════════════
% SECTION C: PERFORMANCE EXPECTANCY
% ═══════════════════════════════════
\noindent{\large\bfseries Section C: Performance Expectancy}\vspace{3pt}

\noindent\begin{tabularx}{\textwidth}{@{}L{0.5cm} X L{5.5cm}@{}}
Q13 & Digital tools help me complete tasks faster than paper. & \likert \\[3pt]
Q14 & Digital tools improve the quality/accuracy of my work. & \likert \\[3pt]
Q15 & Using digital tools increases my overall productivity. & \likert \\[3pt]
Q16 & The digital tools available are well-suited to my actual job tasks. & \likert \\
\end{tabularx}

\vspace{4pt}
% ═══════════════════════════════════
% SECTION D: EFFORT EXPECTANCY
% ═══════════════════════════════════
\noindent{\large\bfseries Section D: Effort Expectancy}\vspace{3pt}

\noindent\begin{tabularx}{\textwidth}{@{}L{0.5cm} X L{5.5cm}@{}}
Q17 & How difficult do you find digital tools to use? & \likert{} {\scriptsize(1=Very Easy, 5=Very Difficult)} \\[3pt]
Q18 & I am confident in my ability to use digital tools for my work. & \likert \\[3pt]
Q19 & Learning to use a new portal/app takes me: & {\Large$\square$} <1 day {\Large$\square$} Few days {\Large$\square$} 1--2 weeks {\Large$\square$} >2 weeks \\[3pt]
Q20 & The design/interface of most government portals is user-friendly. & \likert \\
\end{tabularx}

\vspace{4pt}
% ═══════════════════════════════════
% SECTION E: SOCIAL INFLUENCE
% ═══════════════════════════════════
\noindent{\large\bfseries Section E: Social Influence}\vspace{3pt}

\noindent\begin{tabularx}{\textwidth}{@{}L{0.5cm} X L{5.5cm}@{}}
Q21 & My superiors encourage the use of digital tools. & \likert \\[3pt]
Q22 & My colleagues regularly use digital tools in their work. & \likert \\[3pt]
Q23 & There is a formal mandate/order requiring digital tool use in my department. & {\Large$\square$} Yes {\Large$\square$} No {\Large$\square$} Don't know \\
\end{tabularx}

\vspace{4pt}
% ═══════════════════════════════════
% SECTION F: AWARENESS & USAGE
% ═══════════════════════════════════
\noindent{\large\bfseries Section F: Awareness \& Usage}\vspace{3pt}

\noindent\begin{tabularx}{\textwidth}{@{}L{0.5cm} X L{5.5cm}@{}}
Q24 & Which general tools are you aware of? & {\Large$\square$} e-Office {\Large$\square$} CM Helpline {\Large$\square$} PFMS {\Large$\square$} SPARROW {\Large$\square$} iGOT {\Large$\square$} MP eDistrict \\[3pt]
Q25 & How often do you use digital tools for work? & {\Large$\square$} Daily {\Large$\square$} Weekly {\Large$\square$} Monthly {\Large$\square$} Rarely {\Large$\square$} Never \\[3pt]
Q26 & What percentage of your work is done digitally? & {\Large$\square$} 0--20\% {\Large$\square$} 21--40\% {\Large$\square$} 41--60\% {\Large$\square$} 61--80\% {\Large$\square$} 81--100\% \\
\end{tabularx}

\newpage

% ═══════════════════════════════════
% SECTION G: TRAINING
% ═══════════════════════════════════
\noindent{\large\bfseries Section G: Training \& Capacity Building}\vspace{3pt}

\noindent\begin{tabularx}{\textwidth}{@{}L{0.5cm} X L{5.5cm}@{}}
Q27 & Have you attended any digital skills training in the last 2 years? & \yesno \\[3pt]
Q28 & If yes, how many training sessions? & {\Large$\square$} 1 {\Large$\square$} 2--3 {\Large$\square$} 4--5 {\Large$\square$} More than 5 \\[3pt]
Q29 & Rate the quality of training received: & \likert \\[3pt]
Q30 & Was the training sufficient for your actual job needs? & \likert \\[3pt]
Q31 & What topics need more training? & \rule{\linewidth}{0.4pt}\\[2pt] & & \rule{\linewidth}{0.4pt} \\
\end{tabularx}

\vspace{4pt}
% ═══════════════════════════════════
% SECTION H: CHALLENGES
% ═══════════════════════════════════
\noindent{\large\bfseries Section H: Challenges \& Barriers}\vspace{3pt}

\noindent\begin{tabularx}{\textwidth}{@{}L{0.5cm} X L{5.5cm}@{}}
Q32 & What issues do you face? (tick all) & {\Large$\square$} Slow internet {\Large$\square$} Frequent crashes {\Large$\square$} No device {\Large$\square$} Complex interface {\Large$\square$} No training {\Large$\square$} No support {\Large$\square$} Power cuts \\[3pt]
Q33 & How often do digital issues disrupt your work? & {\Large$\square$} Daily {\Large$\square$} Weekly {\Large$\square$} Monthly {\Large$\square$} Rarely {\Large$\square$} Never \\[3pt]
Q34 & I feel comfortable asking for help with digital tools. & \likert \\[3pt]
Q35 & My organisation provides adequate support for digital tools. & \likert \\[3pt]
Q36 & My department is committed to digital transformation. & \likert \\
\end{tabularx}

\vspace{4pt}
% ═══════════════════════════════════
% SECTION I: RECOMMENDATIONS
% ═══════════════════════════════════
\noindent{\large\bfseries Section I: Recommendations}\vspace{3pt}

\noindent Q37. Rank these priorities (1=highest, 5=lowest):\vspace{4pt}

\noindent\begin{tabularx}{\textwidth}{@{}L{0.5cm} X L{1.5cm}@{}}
& Better internet connectivity & Rank: \_\_\_ \\[3pt]
& More/better devices & Rank: \_\_\_ \\[3pt]
& More training programmes & Rank: \_\_\_ \\[3pt]
& Simpler portal interfaces & Rank: \_\_\_ \\[3pt]
& Faster IT support & Rank: \_\_\_ \\
\end{tabularx}

\vspace{4pt}
\noindent Q38. What one change would most improve your use of digital tools?\vspace{4pt}

\noindent\rule{\textwidth}{0.4pt}\vspace{4pt}
\noindent\rule{\textwidth}{0.4pt}\vspace{4pt}
\noindent\rule{\textwidth}{0.4pt}\vspace{4pt}

\noindent Q39. Has digital tool adoption improved service delivery to citizens?\vspace{2pt}

\noindent {\Large$\square$} Yes, significantly\quad{\Large$\square$} Yes, somewhat\quad{\Large$\square$} No change\quad{\Large$\square$} No, it has worsened\quad{\Large$\square$} Can't say

\vspace{4pt}\noindent\rule{\textwidth}{1pt}\vspace{2pt}
\begin{center}\textit{--- End of Common Schedule (Q1--Q39). Administer department-specific section below. ---}\end{center}
\rule{\textwidth}{0.5pt}

\newpage
% ═══════════════════════════════════
% DEPARTMENT SPECIFIC: REVENUE
% ═══════════════════════════════════
\noindent{\large\bfseries Section J: Department-Specific --- REVENUE}\vspace{4pt}

\small\textit{Administer ONLY to Revenue department respondents.}\vspace{3pt}

\noindent\begin{tabularx}{\textwidth}{@{}L{0.5cm} X L{5.5cm}@{}}
Q40 & Which Revenue tools are you aware of? & {\Large$\square$} Bhulekh/WebGIS {\Large$\square$} RCMS {\Large$\square$} SAARA {\Large$\square$} SAMPADA {\Large$\square$} e-Court {\Large$\square$} None \\[3pt]
Q41 & Has Bhulekh/WebGIS improved land record speed/accuracy? & \likert \\[3pt]
Q42 & How difficult is RCMS to use for case management? & \likert{} {\scriptsize(1=Easy, 5=Difficult)} \\[3pt]
Q43 & What \% of records still require physical paper files? & {\Large$\square$} 0--20\% {\Large$\square$} 21--40\% {\Large$\square$} 41--60\% {\Large$\square$} 61--80\% {\Large$\square$} 81--100\% \\[3pt]
Q44 & How often do citizens expect you to use digital tools? & \likert{} {\scriptsize(1=Never, 5=Daily)} \\
\end{tabularx}

\vspace{3pt}
% ═══════════════════════════════════
% DEPARTMENT SPECIFIC: RURAL DEVELOPMENT
% ═══════════════════════════════════
\noindent{\large\bfseries Section K: Department-Specific --- RURAL DEVELOPMENT}\vspace{4pt}

\small\textit{Administer ONLY to Rural Development respondents.}\vspace{3pt}

\noindent\begin{tabularx}{\textwidth}{@{}L{0.5cm} X L{5.5cm}@{}}
Q45 & Which RD tools are you aware of? & {\Large$\square$} NREGASoft/NMMS {\Large$\square$} e-Gram Swaraj {\Large$\square$} PMAY-G {\Large$\square$} SBM-G {\Large$\square$} Panchayat Darpan {\Large$\square$} PFMS {\Large$\square$} None \\[3pt]
Q46 & How difficult is managing multiple portals? & \likert{} {\scriptsize(1=Easy, 5=Difficult)} \\[3pt]
Q47 & Rate internet at block/panchayat level: & \likert \\[3pt]
Q48 & Has NMMS improved MGNREGA attendance accuracy? & \likert \\[3pt]
Q49 & How much of your day is spent on portal data entry? & {\Large$\square$} <1hr {\Large$\square$} 1--2hr {\Large$\square$} 2--4hr {\Large$\square$} 4+hr {\Large$\square$} Almost all day \\
\end{tabularx}

\vspace{3pt}
% ═══════════════════════════════════
% DEPARTMENT SPECIFIC: FOREST
% ═══════════════════════════════════
\noindent{\large\bfseries Section L: Department-Specific --- FOREST}\vspace{4pt}

\small\textit{Administer ONLY to Forest department respondents.}\vspace{3pt}

\noindent\begin{tabularx}{\textwidth}{@{}L{0.5cm} X L{5.5cm}@{}}
Q50 & Which Forest tools are you aware of? & {\Large$\square$} e-Green Watch {\Large$\square$} AI Alert System {\Large$\square$} GIS/Remote Sensing {\Large$\square$} Forest Offence MIS {\Large$\square$} Nursery MIS {\Large$\square$} None \\[3pt]
Q51 & Has AI alert system improved detection vs manual patrolling? & \likert{}\quad{\Large$\square$} N/A \\[3pt]
Q52 & How difficult are GIS tools to use? & \likert{} {\scriptsize(1=Easy, 5=Difficult)} \\[3pt]
Q53 & GPS device access: & {\Large$\square$} Dept-issued {\Large$\square$} Personal device {\Large$\square$} Not available \\[3pt]
Q54 & How often does poor network prevent digital tool use in the field? & \likert{} {\scriptsize(1=Never, 5=Always)} \\
\end{tabularx}

\vspace{3pt}
% ═══════════════════════════════════
% DEPARTMENT SPECIFIC: HEALTH
% ═══════════════════════════════════
\noindent{\large\bfseries Section M: Department-Specific --- HEALTH}\vspace{4pt}

\small\textit{Administer ONLY to Health department respondents.}\vspace{3pt}

\noindent\begin{tabularx}{\textwidth}{@{}L{0.5cm} X L{5.5cm}@{}}
Q55 & Which Health tools are you aware of? & {\Large$\square$} ANMOL {\Large$\square$} HMIS {\Large$\square$} Nikshay {\Large$\square$} eVIN {\Large$\square$} IHIP {\Large$\square$} ABHA {\Large$\square$} MPCDSR {\Large$\square$} None \\[3pt]
Q56 & Has ANMOL/ABHA improved patient tracking? & \likert \\[3pt]
Q57 & How often do you enter data in BOTH paper AND digital? & \likert{} {\scriptsize(1=Never, 5=Always)} \\[3pt]
Q58 & How reliably does eVIN reflect actual vaccine stock? & \likert{} {\scriptsize(1=Unreliable, 5=Reliable)} \\[3pt]
Q59 & How much does IHIP reporting add to your workload? & \likert{} {\scriptsize(1=None, 5=Significant)} \\
\end{tabularx}

\newpage
% ═══════════════════════════════════
% ROLE-SPECIFIC QUESTIONS
% ═══════════════════════════════════
\noindent{\large\bfseries Section N: Role-Specific Questions}\vspace{3pt}

\noindent\begin{tabularx}{\textwidth}{@{}L{0.5cm} X L{5.5cm}@{}}
Q60 & Your primary interaction with digital tools: & {\Large$\square$} I enter data {\Large$\square$} I review/approve {\Large$\square$} Field verification {\Large$\square$} I don't use them {\Large$\square$} Other \\[3pt]
Q61 & Is there one person who does most portal work for others? & {\Large$\square$} Yes, one person {\Large$\square$} A few share it {\Large$\square$} Everyone does their own {\Large$\square$} N/A \\[3pt]
Q62 & Is the training appropriate for your specific job role? & \likert \\[3pt]
Q63 & When a portal gives an error, what do you do? & {\Large$\square$} Wait for IT {\Large$\square$} Ask colleague {\Large$\square$} Use paper {\Large$\square$} Fix myself {\Large$\square$} Tell supervisor {\Large$\square$} Abandon task \\[3pt]
Q64 & Do senior officers use digital tools themselves? & {\Large$\square$} Yes, themselves {\Large$\square$} Rely on subordinates {\Large$\square$} Mixed {\Large$\square$} Don't know \\[3pt]
Q65 & Have digital tools changed the work expected at your level? & \likert{} {\scriptsize(1=No change, 5=Completely changed)} \\[3pt]
Q66 & Are there digital tasks beyond your current skill level? & {\Large$\square$} Yes {\Large$\square$} No \\[2pt]
 & If yes, which? & \rule{\linewidth}{0.4pt}\\[3pt] & \rule{\linewidth}{0.4pt} \\[3pt]
Q67 & Should training differ based on job level? & {\Large$\square$} Yes {\Large$\square$} Somewhat {\Large$\square$} No, same for all \\[2pt]
 & Why? & \rule{\linewidth}{0.4pt}\\[3pt] & \rule{\linewidth}{0.4pt} \\
\end{tabularx}

\vspace{3pt}\noindent\rule{\textwidth}{1pt}
\begin{center}
{\large\bfseries --- END OF SCHEDULE ---}\\[3pt]
\textbf{Total Questions Administered:} 39 (common) + 5 (department) + 8 (role-specific) = \textbf{52}\\[8pt]
\textbf{Interviewer Notes:}\vspace{4pt}

\rule{\textwidth}{0.4pt}\vspace{4pt}
\rule{\textwidth}{0.4pt}\vspace{4pt}
\rule{\textwidth}{0.4pt}\vspace{4pt}
\rule{\textwidth}{0.4pt}\vspace{12pt}

\textbf{Interviewer Signature:} \rule{5cm}{0.4pt}\qquad\textbf{Date:} \_\_\_/\_\_\_/2026
\end{center}

\end{document}
