\documentclass[10pt,a4paper]{article}
\usepackage[utf8]{inputenc}\usepackage[T1]{fontenc}\usepackage{mathptmx}
\usepackage[margin=0.8cm]{geometry}\usepackage{enumitem}\usepackage{tabularx}
\usepackage{array}\usepackage{booktabs}\usepackage{fancyhdr}\usepackage{setspace}
\usepackage{amssymb}
\pagestyle{fancy}\fancyhf{}
\fancyhead[L]{\small\textbf{AIGGPA --- Health Department}}\fancyhead[R]{\small ID: \_\_\_\_\_\_\_\_}
\fancyfoot[C]{\small Page \thepage}\renewcommand{\headrulewidth}{0.5pt}
\setlength{\headheight}{14pt}\setstretch{1.1}
\newcolumntype{L}[1]{>{\raggedright\arraybackslash}p{#1}}
\newcommand{\likert}{{\Large$\square$}\,1\quad{\Large$\square$}\,2\quad{\Large$\square$}\,3\quad{\Large$\square$}\,4\quad{\Large$\square$}\,5}
\newcommand{\yesno}{{\Large$\square$}\,Yes\quad{\Large$\square$}\,No}
\newcommand{\blank}{\rule{8cm}{0.4pt}}
\begin{document}

\begin{center}
{\Large\bfseries AIGGPA FIELD RESEARCH SCHEDULE}\\[3pt]
{\large\bfseries Health Department}\\[3pt]
{\small Assessment of Digital Tool Usage Among Government Employees}\\[2pt]
{\small AIGGPA Bhopal \quad$\bullet$\quad 2026}
\end{center}
\vspace{4pt}\noindent\rule{\textwidth}{1pt}\vspace{4pt}
\noindent\begin{tabularx}{\textwidth}{@{}L{7cm} L{7cm}@{}}
\textbf{Respondent ID:} \blank & \textbf{Date:} \_\_\_/\_\_\_/2026 \\[3pt]
\textbf{Office:} {\Large$\square$} Head Office\quad{\Large$\square$} District Office & \textbf{Start:} \_\_:\_\_\quad\textbf{End:} \_\_:\_\_ \\[3pt]
\textbf{Interviewer:} \blank & \\
\end{tabularx}
\vspace{4pt}\noindent\rule{\textwidth}{0.5pt}\vspace{4pt}

\noindent\textbf{Key Digital Tools:} ANMOL MP, HMIS, Nikshay (TB), eVIN (Vaccine), IHIP (Surveillance), Ayushman Bharat/ABHA, MPCDSR

\vspace{3pt}

\vspace{4pt}\noindent\rule{\textwidth}{0.5pt}

\vspace{3pt}
\noindent{\large\bfseries Section A: Respondent Profile}\vspace{4pt}

\noindent\begin{tabularx}{\textwidth}{@{}L{0.6cm} L{7.5cm} X@{}}
Q1 & Designation / Post: & \blank \\[3pt]
Q2 & Job Role / Level: & \blank \\[3pt]
Q3 & Age group: & {\Large$\square$} Below 30\quad{\Large$\square$} 30--45\quad{\Large$\square$} 46--60 \\[3pt]
Q4 & Gender: & {\Large$\square$} Male\quad{\Large$\square$} Female\quad{\Large$\square$} Other \\[3pt]
Q5 & Years of service: & {\Large$\square$} 0--5\quad{\Large$\square$} 6--10\quad{\Large$\square$} 11--20\quad{\Large$\square$} 21+ \\[3pt]
Q6 & Highest education: & {\Large$\square$} Up to 12th\quad{\Large$\square$} Graduate\quad{\Large$\square$} PG\quad{\Large$\square$} Professional \\
\end{tabularx}

\vspace{4pt}
\noindent{\large\bfseries Section B: Infrastructure}\vspace{2pt}

\small\textit{Likert: 1=Strongly Disagree/Very Poor \quad 2=Disagree/Poor \quad 3=Neutral \quad 4=Agree/Good \quad 5=Strongly Agree/Excellent}\normalsize\vspace{4pt}

\noindent\begin{tabularx}{\textwidth}{@{}L{0.6cm} X L{5.5cm}@{}}
Q7 & Devices at your workstation: & {\Large$\square$} Desktop {\Large$\square$} Laptop {\Large$\square$} Tablet {\Large$\square$} Phone {\Large$\square$} None \\[3pt]
Q8 & Share device with others? & {\Large$\square$} Yes, always {\Large$\square$} Sometimes {\Large$\square$} No, dedicated \\[3pt]
Q9 & Rate internet connectivity: & \likert \\[3pt]
Q10 & Internet outages per week: & {\Large$\square$} Never {\Large$\square$} 1--2 {\Large$\square$} 3--5 {\Large$\square$} Daily \\[3pt]
Q11 & IT support available? & \yesno \\[3pt]
Q12 & Issue resolution time: & {\Large$\square$} Same day {\Large$\square$} 2--3 days {\Large$\square$} 1 week+ {\Large$\square$} Never \\
\end{tabularx}

\vspace{4pt}
\noindent{\large\bfseries Section C: Performance Expectancy}\vspace{4pt}

\noindent\begin{tabularx}{\textwidth}{@{}L{0.6cm} X L{5.5cm}@{}}
Q13 & Digital tools help me complete tasks faster than paper. & \likert \\[3pt]
Q14 & Digital tools improve accuracy of my work. & \likert \\[3pt]
Q15 & Using digital tools increases my overall productivity. & \likert \\[3pt]
Q16 & Digital tools are well-suited to my actual job tasks. & \likert \\
\end{tabularx}

\vspace{4pt}
\noindent{\large\bfseries Section D: Effort Expectancy}\vspace{4pt}

\noindent\begin{tabularx}{\textwidth}{@{}L{0.6cm} X L{5.5cm}@{}}
Q17 & How difficult are digital tools to use? & \likert{} {\scriptsize(1=Easy, 5=Difficult)} \\[3pt]
Q18 & I am confident using digital tools for work. & \likert \\[3pt]
Q19 & Learning a new portal takes me: & {\Large$\square$} <1 day {\Large$\square$} Few days {\Large$\square$} 1--2 weeks {\Large$\square$} >2 weeks \\[3pt]
Q20 & Government portal interfaces are user-friendly. & \likert \\
\end{tabularx}

\vspace{4pt}
\noindent{\large\bfseries Section E: Social Influence \& Awareness}\vspace{4pt}

\noindent\begin{tabularx}{\textwidth}{@{}L{0.6cm} X L{5.5cm}@{}}
Q21 & Superiors encourage digital tool use. & \likert \\[3pt]
Q22 & Colleagues regularly use digital tools. & \likert \\[3pt]
Q23 & Formal mandate exists for digital tool use? & {\Large$\square$} Yes {\Large$\square$} No {\Large$\square$} Don't know \\[3pt]
Q24 & General tools you know: & {\Large$\square$} e-Office {\Large$\square$} CM Helpline {\Large$\square$} PFMS {\Large$\square$} SPARROW {\Large$\square$} iGOT {\Large$\square$} eDistrict \\[3pt]
Q25 & How often do you use digital tools? & {\Large$\square$} Daily {\Large$\square$} Weekly {\Large$\square$} Monthly {\Large$\square$} Rarely {\Large$\square$} Never \\[3pt]
Q26 & Percentage of work done digitally: & {\Large$\square$} 0--20\% {\Large$\square$} 21--40\% {\Large$\square$} 41--60\% {\Large$\square$} 61--80\% {\Large$\square$} 81--100\% \\
\end{tabularx}

\newpage
\noindent{\large\bfseries Section F: Training}\vspace{4pt}

\noindent\begin{tabularx}{\textwidth}{@{}L{0.6cm} X L{5.5cm}@{}}
Q27 & Digital training in last 2 years? & \yesno \\[3pt]
Q28 & If yes, how many sessions? & {\Large$\square$} 1 {\Large$\square$} 2--3 {\Large$\square$} 4--5 {\Large$\square$} 5+ \\[3pt]
Q29 & Rate training quality: & \likert \\[3pt]
Q30 & Training sufficient for your job? & \likert \\[3pt]
Q31 & Topics needing more training: & \rule{\linewidth}{0.4pt}\\[3pt] & \rule{\linewidth}{0.4pt} \\
\end{tabularx}

\vspace{4pt}
\noindent{\large\bfseries Section G: Challenges}\vspace{4pt}

\noindent\begin{tabularx}{\textwidth}{@{}L{0.6cm} X L{5.5cm}@{}}
Q32 & Issues faced (tick all): & {\Large$\square$} Slow net {\Large$\square$} Crashes {\Large$\square$} No device {\Large$\square$} Complex UI {\Large$\square$} No training {\Large$\square$} No support {\Large$\square$} Power cuts \\[3pt]
Q33 & How often do digital issues disrupt work? & {\Large$\square$} Daily {\Large$\square$} Weekly {\Large$\square$} Monthly {\Large$\square$} Rarely {\Large$\square$} Never \\[3pt]
Q34 & Comfortable asking for digital help? & \likert \\[3pt]
Q35 & Organisation supports digital tools adequately? & \likert \\[3pt]
Q36 & Department committed to digital transformation? & \likert \\
\end{tabularx}

\vspace{4pt}
\noindent{\large\bfseries Section H: Recommendations}\vspace{4pt}

\noindent Q37. Rank priorities (1=highest, 5=lowest):\vspace{3pt}

\noindent\begin{tabularx}{\textwidth}{@{}L{0.6cm} X L{1.5cm}@{}}
& Better internet & Rank: \_\_\_ \\[2pt]
& More/better devices & Rank: \_\_\_ \\[2pt]
& More training & Rank: \_\_\_ \\[2pt]
& Simpler portals & Rank: \_\_\_ \\[2pt]
& Faster IT support & Rank: \_\_\_ \\
\end{tabularx}

\vspace{3pt}
\noindent Q38. What one change would most improve your digital tool use?\vspace{3pt}

\noindent\rule{\textwidth}{0.4pt}\vspace{3pt}\rule{\textwidth}{0.4pt}\vspace{3pt}

\noindent Q39. Has digital adoption improved service delivery to citizens?\vspace{2pt}

\noindent {\Large$\square$} Yes, significantly\quad{\Large$\square$} Somewhat\quad{\Large$\square$} No change\quad{\Large$\square$} Worsened\quad{\Large$\square$} Can't say

\vspace{4pt}\noindent\rule{\textwidth}{1pt}\vspace{2pt}
\begin{center}\textit{--- End of Common Questions (Q1--Q39). Department-specific section follows. ---}\end{center}
\rule{\textwidth}{0.5pt}
\newpage
\noindent{\large\bfseries Section I: Health Department --- Specific Questions}\vspace{4pt}

\noindent\begin{tabularx}{\textwidth}{@{}L{0.6cm} X L{5.5cm}@{}}
Q40 & Which Health department digital tools are you aware of? & {\Large$\square$} ANMOL {\Large$\square$} HMIS {\Large$\square$} Nikshay {\Large$\square$} eVIN {\Large$\square$} IHIP {\Large$\square$} ABHA {\Large$\square$} MPCDSR {\Large$\square$} None \\[3pt]
Q41 & Has ANMOL MP or ABHA Health IDs improved your ability to track patients across visits? & \likert \\[3pt]
Q42 & How often do you enter the SAME data in both paper registers AND digital systems (HMIS, ANMOL)? & \likert{} {\scriptsize(1=Never, 5=Always)} \\[3pt]
Q43 & How reliably does eVIN reflect actual vaccine stock and cold chain temperature at your facility? & \likert{} {\scriptsize(1=Very Unreliable, 5=Very Reliable)} \\[3pt]
Q44 & How much does mandatory IHIP disease reporting add to your daily workload? & \likert{} {\scriptsize(1=No burden, 5=Significant burden)} \\[3pt]
Q45 & When registering a new pregnant woman for ANC, which steps are on ANMOL and which on paper? & On ANMOL: \rule{6cm}{0.4pt}\\[2pt] && On paper: \rule{6cm}{0.4pt} \\[3pt]
Q46 & For Nikshay (TB portal): do you enter case notifications yourself or does someone else do it? & {\Large$\square$} I enter myself {\Large$\square$} DEO enters {\Large$\square$} Someone at district {\Large$\square$} Don't use Nikshay {\Large$\square$} Not applicable \\[3pt]
Q47 & When there is a disease outbreak (malaria, dengue), how do you report it? & {\Large$\square$} IHIP portal immediately {\Large$\square$} Phone call to BMO first {\Large$\square$} Paper form to CMHO {\Large$\square$} WhatsApp message {\Large$\square$} Multiple methods \\[3pt]
Q48 & As an ANM / Staff Nurse / MO, what is the single biggest problem with health portals? & \rule{\linewidth}{0.4pt}\\[2pt] && \rule{\linewidth}{0.4pt} \\[3pt]
Q49 & Does the BMO / CMHO review the data you upload on HMIS / ANMOL? & {\Large$\square$} Reviews regularly {\Large$\square$} Checks sometimes {\Large$\square$} Only during inspections {\Large$\square$} Never {\Large$\square$} Don't know \\[3pt]
\end{tabularx}

\vspace{4pt}
\noindent{\large\bfseries Section J: Role-Specific Questions}\vspace{4pt}

\noindent\begin{tabularx}{\textwidth}{@{}L{0.6cm} X L{5.5cm}@{}}
Q50 & Primary interaction with digital tools: & {\Large$\square$} Data entry {\Large$\square$} Review/approve {\Large$\square$} Field verification {\Large$\square$} Don't use {\Large$\square$} Other \\[3pt]
Q51 & One person does most portal work for others? & {\Large$\square$} Yes, one person {\Large$\square$} A few share {\Large$\square$} Everyone does own {\Large$\square$} N/A \\[3pt]
Q52 & Training appropriate for your specific job role? & \likert \\[3pt]
Q53 & When a portal errors out, you: & {\Large$\square$} Wait for IT {\Large$\square$} Ask colleague {\Large$\square$} Use paper {\Large$\square$} Fix myself {\Large$\square$} Tell supervisor {\Large$\square$} Abandon \\[3pt]
Q54 & Senior officers use digital tools themselves? & {\Large$\square$} Yes {\Large$\square$} Rely on subordinates {\Large$\square$} Mixed {\Large$\square$} Don't know \\[3pt]
Q55 & Digital tools changed work expected at your level? & \likert{} {\scriptsize(1=No change, 5=Completely)} \\[3pt]
Q56 & Digital tasks beyond your current skill? & {\Large$\square$} Yes {\Large$\square$} No\quad If yes: \rule{4cm}{0.4pt} \\[3pt]
Q57 & Training should differ based on your job level? & {\Large$\square$} Yes {\Large$\square$} Somewhat {\Large$\square$} No\quad Why: \rule{3.5cm}{0.4pt} \\
\end{tabularx}

\vspace{3pt}\noindent\rule{\textwidth}{1pt}
\begin{center}
{\large\bfseries --- END OF SCHEDULE ---}\\[2pt]
\textbf{Total: 39 (common) + 10 (Health) + 8 (role) = 57 questions}\\[8pt]
\textbf{Notes:}\vspace{3pt}

\rule{\textwidth}{0.4pt}\vspace{3pt}
\rule{\textwidth}{0.4pt}\vspace{3pt}
\rule{\textwidth}{0.4pt}\vspace{3pt}
\rule{\textwidth}{0.4pt}\vspace{4pt}

\textbf{Interviewer:} \rule{5cm}{0.4pt}\qquad\textbf{Date:} \_\_\_/\_\_\_/2026
\end{center}
\end{document}
